Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2019-12-09 xrb/paper.tex
close marginpar

All simulations use adaptive mesh refinement to refine on the
atmosphere (leaving the space between the top of the atmosphere and
upper boundary at low resolution). As seen in Figure \ref{fig:grids}, 
\MarginPar{Can we change the black grids to magenta? Black is hard to see against the dark red and black background.}
we use up to 3 refinement levels in addition to the base grid, the first
one a factor of 4 finer than the previous and the remaining each a
factor of 2 finer than the previous. \castro\ subcycles in time, so the 
finer grids are evolved with a finer timestep than the coarse grids. 
Occasionally, the timestep chosen at the start of a cycle will violate
the CFL condition during the advancement of the finer grids. In this
case, we restart the finer grid evolution with a smaller timestep,
subcycling within the larger timestep hierarchy.  We use a CFL number
of 0.8 for our simulations.  
% \MarginPar{true for all?} 
The base grid for our standard
simulations is $768\times 192$ zones, and the equivalent finest grid
when 3 refinement levels are added would be $12288\times 3072$ zones.
Our standard domain is $1.2288\times 10^5~\mathrm{cm} \times
3.072\times 10^4~\mathrm{cm}$, corresponding to $10~\mathrm{cm}$ resolution
on the finest grid.  We only refine the fuel layer in the left half of
the domain at the highest resolution (and only down to densities of
$2.5\times 10^4~\gcc$), since this is where we expect the flame to
propagate.  At the start of the simulation, $3.4\%$ of the domain is
at the finest resolution.  This increases to $7.4\%$ by the end of the
simulation, because of the increase in the scale height of the atmosphere
behind the flame.

>>>>

All simulations use adaptive mesh refinement to refine on the
atmosphere (leaving the space between the top of the atmosphere and
upper boundary at low resolution). As seen in Figure \ref{fig:grids}, 
we use up to 3 refinement levels in addition to the base grid, the first
one a factor of 4 finer than the previous and the remaining each a
factor of 2 finer than the previous. \castro\ subcycles in time, so the 
finer grids are evolved with a finer timestep than the coarse grids. 
Occasionally, the timestep chosen at the start of a cycle will violate
the CFL condition during the advancement of the finer grids. In this
case, we restart the finer grid evolution with a smaller timestep,
subcycling within the larger timestep hierarchy.  We use a CFL number
of 0.8 for our simulations.  
% \MarginPar{true for all?} 
The base grid for our standard
simulations is $768\times 192$ zones, and the equivalent finest grid
when 3 refinement levels are added would be $12288\times 3072$ zones.
Our standard domain is $1.2288\times 10^5~\mathrm{cm} \times
3.072\times 10^4~\mathrm{cm}$, corresponding to $10~\mathrm{cm}$ resolution
on the finest grid.  We only refine the fuel layer in the left half of
the domain at the highest resolution (and only down to densities of
$2.5\times 10^4~\gcc$), since this is where we expect the flame to
propagate.  At the start of the simulation, $3.4\%$ of the domain is
at the finest resolution.  This increases to $7.4\%$ by the end of the
simulation, because of the increase in the scale height of the atmosphere
behind the flame.
